Which ITG Stepcharts are Turniest?

### 2016-03-15 itg/paper.tex
Add some important new citations
team dragonforce

Stepcharts are rated in difficulty on a scale from 1 to 20 ``feet'' \cite{simplylove}\footnote{
Other dance games \cite{konami}, which shall remain unnamed, feature wimpier stepcharts rated only up to 10, but as ITG players got better, they left those charts in the dust and began creating their own charts to challenge themselves with ridiculous difficulties. This paper's author plays ITG at the 13-14 level.}.
To date, difficulty is always judged by a human (typically the step author), and primarily reflects factors such as burstiness (footspeed), prolongedness of streams (stamina), and complexity of jumps, holds, and crossovers (technical).
These measures of difficulty have been well-studied in prior works \cite{callofthehound,dawgsinthehouse}.

@@

Of course, composing a stepchart of nothing but the theoretically-turniest patterns would be extremely tiresome (in more ways than one).
We turn our attention to existing ITG charts which were developed prior to this study, to investigate how much ITG players turn in the real world.
We processed every stepchart in our collection, which includes 70+ song packs.
Most well-known pack series from the ITG community are included, such as {\em Cirque}, {\em ITG}, {\em Mute Sims}, {\em Pendulum}, {\em r21*}, {\em SPEEDCOOOORE}, {\em The Legend of Zim}, {\em Valex's Magical 4-Arrow Adventure}, and {\em Oh Henry! Mad Stamina: Streamy $\cdot$ Brutal $\cdot$ Stamina Bar in Milk Chocolate}.

@@

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=0.48\textwidth]{machine-translation.jpg}
	\end{center}
	\caption{We employ the techniques of \cite{deltax} for ITG machine translation.} %All photos credit \cite{alanv}.
	\label{fig:machine-translation}
\end{figure}
\bibliographystyle{abbrvnat}
\bibliography{citations}

>>>>

Stepcharts are rated in difficulty on a scale from 1 to 20 ``feet'' \cite{simplylove}\footnote{
Other dance games, which shall remain unnamed, but whose initials are \cite{konami}, feature wimpier stepcharts rated only up to 10. As ITG players got better, they left those charts in the dust and began creating their own charts to challenge themselves with ridiculous difficulties. This paper's author plays ITG at the 13-14 level.}.
To date, difficulty is judged by a human (typically the step author), and primarily reflects factors such as burstiness ({\em footspeed}), prolongedness of streams ({\em stamina}), and complexity of jumps, holds, and crossovers ({\em technical}).
These measures of difficulty have been well-studied in prior works \cite{teamdragonforce,callofthehound,dawgsinthehouse}.

@@

Of course, composing a stepchart of nothing but the theoretically-turniest patterns would be extremely tiresome (in more ways than one).
We turn our attention to existing ITG charts which were developed prior to this study, to investigate how much ITG players turn in the real world.
We processed every stepchart in our collection, which includes 70+ song packs.
Most well-known pack series from the ITG community are included, such as {\em Cirque}, {\em ITG}, {\em Mute Sims}, {\em Pendulum}, {\em r21*}, {\em SPEEDCOOOORE}, {\em Tachyon}, {\em The Legend of Zim}, {\em Valex's Magical 4-Arrow Adventure}, and {\em Oh Henry! Mad Stamina: Streamy $\cdot$ Brutal $\cdot$ Stamina Bar in Milk Chocolate}.

@@

\begin{figure}[h]
	\begin{center}
	\includegraphics[width=0.48\textwidth]{machine-translation.jpg}
	\end{center}
	\caption{We employ the techniques of \cite{deltax} for ITG machine translation \cite{itg-translation1,itg-translation2}.} %All photos credit \cite{alanv}.
	\label{fig:machine-translation}
\end{figure}
\bibliographystyle{abbrvnat}
\bibliography{citations}
